SRG operator evolution

### 2019-06-03 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Updated SRG operator evolution notes.
Added brief descriptions of how to numerically compute momentum projection operators and distributions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: srg_operator_evolution.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: May 20, 2019
%
% Notes on SRG operator evolution project.
%
% Revision history:
% 	May 31, 2019 - Renamed to srg_operator_evolution.tex from operator_evolution_May20.tex. Added a description of computing SRG unitary
%                              transformations. Added momentum projection operator contours and momentum distribution plots.                            
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

@@

Organize this according to the figures: what story do the figures tell? Format should be description of the calculation, followed by the figure, followed by takeaways.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: srg_operator_evolution.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: May 20, 2019
%
% Notes on SRG operator evolution project.
%
% Revision history:
% 	05/31/19 --- Renamed magnus.tex from magnus_Jan08.tex. - Renamed to srg_operator_evolution.tex from operator_evolution_May20.tex.
%			   Added a description of computing SRG unitary transformations. Added momentum projection operator contours and momentum %                         distribution plots.
%	06/03/19 --- Added brief descriptions of how to numerically compute momentum projection operators and distributions.                           
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Applying $a^{\dagger}_q a_q$ to a wave function $\psi(k)$ returns $\psi(q)$. For the discrete case, $\psi(k_i)$ is an $N \times 1$ vector and $a^{\dagger}_q a_q (k_i, k_j)$ is an $N \times N$ matrix where $i$, $j=1$, ... , $N$. Then $a^{\dagger}_q a_q$ acting on $\psi(k)$ is a matrix multiplication, implying a continuous integration over $d^3k$. Therefore, we include a factor of $1 / (k^2 dk) \implies 1 / (k_i k_j \sqrt{w_i w_j})$ in $a^{\dagger}_q a_q (k_i, k_j)$ where $w$ represents the momentum weights. In matrix form,

\begin{eqnarray}
	\label{eq:momentum_projection_operator}
	a^{\dagger}_q a_q (k_i, k_j) = \frac{\delta_{k_i q} \delta_{k_j q}}{k_i k_j \sqrt{w_i w_j}},
\end{eqnarray}

which has units fm$^3$. To evolve operators, we apply $U(s)$ at this point. For mesh-independent figures, we must divide by an additional factor of $k_i k_j \sqrt{w_i w_j}$.

@@

We diagonalize the Hamiltonian for eigenvectors $\phi_{\alpha}$. In the $^{3}S_1$-$^{3}D_1$ coupled channel, the S-component is given by $\phi_{\alpha}[:N]$ and the D-component by $\phi_{\alpha}[N:]$ where $N$ is the length of the momentum mesh. Then the momentum distribution is given by,

\begin{eqnarray}
	\label{eq:momentum_distribution}
	|\phi(k)|^2 = |\phi_{\alpha}[:N]|^2 + |\phi_{\alpha}[N:]|^2.
\end{eqnarray}

This satisfies the normalization condition $\sum_{i=1}^N |\phi(k_i)|^2 = 1$, implying that the factor $k^2 dk$ (or in the discrete case $k_i^2 w_i$) is factored into the wave function. For mesh-independent figures, divide by $k_i^2 w_i$.

@@

Organize this according to the figures. Format should be description of the calculation (previous section), followed by the figure, followed by takeaways.

@@

\textcolor{red}{Add takeaways for these figures.}
